How Slow do my Transient Typechecks Go?

### 2019-08-17 paper.tex
Added a set of contributions to the intro
Signed-off-by: Stefan Marr <git@stefan-marr.de>

This paper builds upon our recent work on optimising transient
type checks \cite{Roberts2017,roberts-and-co-ecoop-2019} by
investigating how benchmark results can be repurposed to identify which
particular transient type checks are resistant to optimisation.
The next section discusses dynamic type checks and gradual typing in
Moth (an implementation of the Grace language), then section~\ref{s-eval} describes our benchmarking protocol. Section~\ref{s-overall} then presents the overall results of
our benchmarks, while section~\ref{s-individual}
looks at the results of benchmarking individual type checks.
Section~\ref{s-rel} presents some additional related work, and finally \ref{s-concl} summarises our results, and briefly considers threats to validity.

>>>>

This paper builds upon our recent work on optimising transient
type checks \cite{Roberts2017,roberts-and-co-ecoop-2019} by
investigating how benchmark results can be repurposed to identify which
particular transient type checks are resistant to optimisation.

Specifically, the contributions of this work are:

\begin{itemize}
  \item an approach to identify gradual type annotations
        that cause significant performance effects
  \item adapting the Takikawa protocol for languages and implementations
        where performance effects are dominated by type annotations instead
        of transitions between typed and untyped modules
  \item observing that performance of small benchmarks
        with 10--250 type annotations is dominated by only
        one or two type annotations
\end{itemize}

The next section discusses dynamic type checks and gradual typing in
Moth (an implementation of the Grace language), then section~\ref{s-eval} describes our benchmarking protocol. Section~\ref{s-overall} then presents the overall results of
our benchmarks, while section~\ref{s-individual}
looks at the results of benchmarking individual type checks.
Section~\ref{s-rel} presents some additional related work, and finally \ref{s-concl} summarises our results, and briefly considers threats to validity.
